Fermi and eROSITA bubbles

### 2021-10-23 paper.tex
update

\section{Methodology}
\subsection{Assumptions and Numerical Techniques}
\begin{enumerate}
  \item \textsc{gamer-sr}
    \begin{enumerate}
      \item GPU acceleration.
      \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
            significantly reducing numerical error caused by the non-relativistic cold disk.
    \end{enumerate}
  \item Cosmic-ray
    \begin{enumerate}
      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
            as a function of $\mathbf{r}$ and $t$.
      \item We did not model the CR energy spectrum.
      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
            and inverse Compton emission, and reacceleration in shocks.
      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
      \item We have assumed $\mathbf{B}$ is zero within the simulation box as the field inside\
            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
            little effect on the overall dynamics.\
            It might somewhat affect the instabilities near the bubble's surface, but that's a secondary effect.
      \item Since $\mathbf{B}$ is zero, we can also ignore the effect of cosmic-ray diffusion.
    \end{enumerate}
  \item Gravity
    \begin{enumerate}
      \item Since , we have assumed the 
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.

@@

\begin{enumerate}
\item Gravitational potential
  \begin{enumerate}
    \item Isothermal slab
    \item NFW potential
  \end{enumerate}

\item Cold disk
  \begin{enumerate}
    \item The fractal density is created using the publicly\
          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}}.
    \item
  \end{enumerate}
\end{enumerate}

\subsection{Jet injection}

\subsection{X-ray and Gamma-ray emission}
  \begin{enumerate}
    \item X-ray
       \begin{enumerate}
         \item
       \end{enumerate}
    \item Gamma-ray
       \begin{enumerate}
         \item
       \end{enumerate}
  \end{enumerate}

>>>>

\section{Methodology}
\subsection{Assumptions and Numerical Techniques}
\begin{enumerate}
  \item Numerical features:
    \begin{enumerate}
      \item GPU acceleration with the \textsc{gamer-sr} code.
      \item Special relativistic hydrodynamics.
      \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
            significantly reducing numerical error caused by the non-relativistic cold disk.
    \end{enumerate}
  \item Assumptions on cosmic-ray:
    \begin{enumerate}
      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
            as a function of $\mathbf{r}$ and $t$.
      \item We did not model the CR energy spectrum.
      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
            and inverse Compton emission, and reacceleration in shocks.
      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
      \item We have assumed $\mathbf{B}$ is zero within the simulation box as the field inside\
            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
            little effect on the overall dynamics.\
            It might somewhat affect the instabilities near the bubble's surface, but that's a secondary effect.
      \item Since $\mathbf{B}$ is zero, we can also ignore the effect of cosmic-ray diffusion.
    \end{enumerate}
  \item Assumptions on gravity:
    \begin{enumerate}
      \item The ISM disk and atmosphere are subjected to the fixed external potential of bulge.
      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
      \item We ignore the Milky Way rotation.
      \item We use the potential of isothermal slab to mimic the fixed gravitational potential of the stellar bulge.
      \item The interface between cold ISM disk and atmosphere is parallel to galactic plane and is pressure balanced.
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.

@@

\begin{enumerate}
\item Fixed externel gravitational potential:
  \begin{enumerate}
    \item Bulge:
      \begin{enumerate}
       \item Peak density: $\rho_{\text{bulge}}^{\text{peak}}=4\times 10^{-24}$ g/cm$^3$.
       \item Potential (isothermal slab):
         \begin{equation}
           \Phi_{\text{bulge}}=\
           2\sigma^2_{\text{bulge}}\
           \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right),
         \end{equation}
          where $\displaystyle \sigma_{\text{bulge}}=\
                \sqrt{\frac{k_{B}T_{\text{bulge}}}{m}}=100$ km/s \citep{velocity-dispersion-MW}.
      \end{enumerate}

    \item Dark logarithmic halo:
         \begin{equation}
           \Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right),
         \end{equation}
         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc.

  \end{enumerate}

\item Clummpy cold disk:
  \begin{enumerate}
    \item Scale height: $z_{0}=100$ pc. \citep{paek-ism-density}
    \item Peak density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
    \item $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
    \item Density:
          \begin{equation}
             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{disk}}/m}\right].
             \label{disk-density}
          \end{equation}

    \item The fractal density is created using the publicly\
          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  \end{enumerate}

\item Isothermal atmosphere:
  \begin{enumerate}
     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
     \item Density:
          \begin{equation}
             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
             \exp\left[-\frac{\Phi_{\text{bulge}}}{k_{B}T_{\text{atmp}}/m}\right],
             \label{atmosphere-density}
          \end{equation}
          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
          and gravitational potential are continuous at the interface between disk and atmosphere (i.e. $z=\pm z_{0}$).
  \end{enumerate}

\end{enumerate}
\subsection{Jet injection}

\subsection{X-ray and Gamma-ray emission}
  \begin{enumerate}
    \item X-ray:
       \begin{enumerate}
         \item Thermal bremsstrahlung:
       \end{enumerate}
    \item Gamma-ray:
       \begin{enumerate}
         \item Hadronic process:
       \end{enumerate}
  \end{enumerate}
